% LaTeX resume using res.sty
\documentstyle[fancyhead]{res}
% Use \documentstyle[fancyhead,newcent]{res} to get New Century Schoolbook
% Postscript font; the fancyhead option is used to get 2 line header
% Use \documentstyle[fancyhead]{res} to get default (Computer Modern) font
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headrulewidth}{0pt} % suppress line drawn by default with fancyhead
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header

%\lhead{\hspace*{-\sectionwidth}Brenda Baud} % force lhead all the way left
%\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document
\begin{document} 

% Center the name over the entire width of resume:
\moveleft.5\hoffset\centerline{\large\bf Intai Huang}
% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
\moveleft.5\hoffset\centerline{100A Owairaka Ave.}
\moveleft.5\hoffset\centerline{Mt. Albert, Auckland}
\vspace{0.1in}
\moveleft.5\hoffset\centerline{Mobile: (021) 107 5713}
\moveleft.5\hoffset\centerline{Email: intai.hg@gmail.com}

\begin{resume}
\vspace{0.1in}
 
\section{SKILLS PROFILE} 
\vspace{0.1in}

I am a software developer and architect with 20+ years of experience delivering applications across web, mobile, and embedded platforms. I have expertise in JavaScript, Dart, C/C++, Objective-C, and PHP, with a foundation in computer graphics using OpenGL and DirectX. My career spans game development on the Sony PlayStation Portable, large-scale web applications, and more recently, AI agentic software development for delivering production-ready solutions.

\section{PERSONAL PROJECTS} 
\vspace{0.1in}

Published an agentic development workflow as a Claude Code plugin in marketplaces \\
(https://claudemarketplaces.com) to automate and streamline software development, from story planning to fully tested implementation. The plugin is open-sourced on GitHub (https://github.com \\
/Intai/story-flow).

Developed CyphrIM, a distributed messaging web app built on GUN (https://gun.eco), an open-source distributed graph database. All messages are encrypted using public keys and synchronised directly peer-to-peer between browsers. Because of encryption and decentralisation, no server stores or owns user data. The application is open-sourced on GitHub (https://github.com/Intai/cyphrim-com).

Created Bdux, a Flux architecture inspired by Bacon.js, Redux, and React, released as an open-source npm package (https://www.npmjs.com/\%7Eintai). Bdux is fully reactive from action to React component and supports Redux-style time travel via middleware and reducers. It also enables universal rendering through middleware.

Developed MyRadio, a podcast management app using AngularJS, Bacon.js, Underscore.js, Traceur, Sass, Browserify, Gulp, and Firebase. Experimented with applying the Facebook Flux dispatcher concept in AngularJS and focused on creating directives to minimise view-controller logic.

Developed and hosted PixPrism using Symfony2, MySQL, Sass, RequireJS, and Puppet on EC2 and S3 to generate mobile-friendly photo galleries for any website.

\section{WORK HISTORY and EXPERIENCE} 
\vspace{0.15in} 

\hspace*{-0.25in} 2025 Jun - Present,\\
\hspace*{-0.25in} Software Architect at PDI Technologies

The Mobile Experience Manager (MEM) Portal enables tenants to configure templates, themes, features, and layouts without coding, allowing them to customise their mobile applications with ease. Changes can be previewed and published over the air (OTA), reducing setup time and dependency on engineering teams. It's a Next.js application built with Zustand and Zod.

Implemented an agentic development workflow leveraging AI (Claude Code) for story planning, task dependency analysis, implementation, code review, and automated BDD scenario execution, including Playwright scripts for regression testing, enabling rapid delivery of fully tested, production-ready software.

\newpage
\vspace{0.15in} 

\hspace*{-0.25in} 2022 Aug - 2025 Jun,\\
\hspace*{-0.25in} Software Architect at P97 Networks

The Fleet360 Portal helps companies monitor vehicle usage, assign drivers, track fuel usage, and detect fraud, allowing businesses to make informed decisions that lower costs and improve efficiency. It's a greenfield product that we setup from the ground up. Everyone on the scrum team is full-stack; however, my responsibilities focus on frontend development. It's a typical React single-page application with GraphQL. GraphQL is part of the architecture because we plan to introduce microservices as the product scales. It provides a clean way to aggregate independent, loosely coupled services for frontend consumption. Additionally, a Flutter companion app enables payments at petrol stations.

Applied established frontend practices such as structured state management and reactive, functional programming (Redux, RxJS, Ramda), with containerisation to ensure consistent development and deployment (Docker). Ensured product quality through enforced linting, 100\% unit test coverage, automated integration and end-to-end (E2E) testing, and visual regression testing, aligned with the testing pyramid.

Managed the two-week Scrum cycle, including design sessions, shaping technical requirements for Jira stories, and facilitating ceremonies (grooming, team refinement, and retrospectives) to align the team on feature delivery.

\hspace*{-0.25in} 2018 Nov - 2022 Jul,\\
\hspace*{-0.25in} Senior Software Architect at ProjectManager.com

The ProjectManager.com web app features complex UI functionality, including a custom spreadsheet, drag-and-drop interfaces, and real-time updates via Socket.IO. New frontend features were implemented using React, Bacon.js, and Ramda, supported by a reusable base component library. Maintaining and extending the app required working across old and new codebases, with iframes used to encapsulate server-rendered pages.

There are two squads with around six frontend-focused and two backend-focused developers. I am responsible for elaborating epics and stories with product owners and the design team, slicing stories into smaller testable units, and planning technically to enable developers to work in parallel without blocking each other. I also provide feedback in pull requests through code reviews and participate in day-to-day technical discussions.

I also made initiative to setup CI/CD for third party integrations using Docker, Amazon CodeBuild, ECR, ECS, CodeDeploy and CodePipeline. CloudFormation templates were written for documentation and repeatable infrastructure, ensuring consistent deployment environments.

\hspace*{-0.25in} 2018 May - 2018 Oct,\\
\hspace*{-0.25in} Senior Developer at Vodafone

Took on a contract to work on the MyVodafone self-service app in React Native. The Redux reducers were maintainable, readable, and easy to unit test, allowing us to achieve at least 100\% test coverage. Redux-Saga was used both before and after the reducers, which, in my opinion, was abused and became difficult to manage.

\hspace*{-0.25in} 2016 Sep - 2018 Apr,\\
\hspace*{-0.25in} Senior Developer at ProjectManager.com

Started working at ProjectManager.com to create a new web app for hybrid project management between Agile and Waterfall. Technically switching from server side rendered JQuery codebase to a React single-page app. To meet MVP timelines, the approach enabled both codebases to coexist rather than pursuing a full rewrite.

\newpage
\vspace{0.15in} 

\hspace*{-0.25in} 2015 May - 2016 Aug,\\
\hspace*{-0.25in} Senior Developer at Vodafone

Worked on the MyVodafone web app. The JavaScript codebase used AngularJS 1.2 and Bootstrap 3, with extensive reliance on jQuery plugins. The integrations between these technologies were fragile, and the widespread use of global scope and large controllers made the application difficult to maintain. Refactored the codebase by removing global scope usage and breaking down directives into more modular components, significantly improving maintainability and readability.

\hspace*{-0.25in} 2014 Jul - 2015 Apri,\\
\hspace*{-0.25in} Developer at Findly

Worked at Findly on the Pollinator project to capture job applicants' details directly, and on CXApply to acquire applicants from other ATS (Applicant Tracking Systems) by providing mobile-friendly versions of their websites. The codebase suffered from limitations of frameworks like AngularJS, including complex and tightly coupled view-model relationships -- an issue later addressed by React and Flux.

\hspace*{-0.25in} 2011 Jun - 2014 Jul,\\
\hspace*{-0.25in} Developer at GrabOne

Started working at GrabOne, responsible for the iOS native wrapper and mobile sites. The native side involved Keychain, Passbook, and Reminders integrations, as well as cookies management, location services, and push notifications. The web side used Symfony 1.4 and a forked jQuery Mobile with GrabOne-specific optimisations. Offline capability was achieved using the HTML5 application cache. Scrolling and keyframe animations were implemented using CSS transitions and JavaScript.

Developed the GrabOne merchant app for iOS using Auto Layout, Core Data, and the ZBar library. The app consumes JSON responses from API and supports offline functionality for unstable internet connections.

\hspace*{-0.25in} 2010 Jul - 2011 Jun,\\
\hspace*{-0.25in} Team Lead at Fishpond

Led the release team to improve the stability of customer sites and internal tools. The team consisted of three QAs and one developer who managed the release process and maintained Nagios alerts. QAs performed manual testing and automated regression tests using Selenium across multiple browsers. Conducted performance testing with XHProf and Circonus, and load testing with JMeter. As team leader, coordinated end-user testing for internal tools with other departments. Authored outage reports detailing what went wrong, how to prevent future incidents, and how to detect issues earlier.

The team later expanded beyond release management to include three additional overseas developers. Coordinating efficiently across different time zones using email and task/bug tracking systems proved to be a significant challenge.

\hspace*{-0.25in} 2010 Jan - 2010 Apr,\\
\hspace*{-0.25in} Developer at Fishpond

Started working at Fishpond, supporting sites with approximately 20 million listed products and 100,000 daily page views. Developed in PHP using both Zend Framework and legacy scripts. The customer team handled backend logic for customer-facing sites and Solr search indexing. Temporarily acted as customer team lead for two to three months due to a promotion, responsible for clarifying requirements, breaking tasks into subtasks, providing technical direction, and performing code reviews.

\newpage
\vspace{0.15in} 

\hspace*{-0.25in} 2007 Jul - 2010 Jan,\\
\hspace*{-0.25in} Developer at Navman

Worked at Navman Technology, which designs Personal Navigation Devices. Gained experience with Component Object Model (COM) architecture, well-suited for Navman's international, multi-site team structure, providing robust and extensible interfaces while hiding implementation details. Utilised the Model-View-Controller (MVC) design pattern to present and process user interactions from the map display.

Worked on a newly designed UI inspired by IDEO (http://ideo.com), featuring iPhone-like scrolling and the ability to access the map anywhere, anytime. Smooth performance was a key requirement, so significant effort was made to optimise class inheritance, streamline low-level rendering, and fine-tune the interface for resistive and capacitive touch screens separately.

\hspace*{-0.25in} 2006 Jan- 2007 June,\\
\hspace*{-0.25in} Developer at Metia Interactive

The Cube project officially started with four programmers and four artists. The game features single-player and two-player (AdHoc) modes, as well as a level editor. The Cube Game was published in the USA, Europe, and Japan (https://en.wikipedia.org/wiki/Cube\%3A\_3D\_Puzzle\_Mayhem).

Programmed the Cube Game for the Windows platform using DirectX with programmable vertex and pixel shaders. Added new features, including lighting and shadows, to prepare the Windows version for Xbox 360.

\hspace*{-0.25in} 2004 - 2005 Feb,

Completed a master thesis on image-based model simplification, implementing a DirectX application to test the hypothesis. Presented the paper at IVCNZ '04.

\hspace*{-0.25in} 2003 - 2004,

Designed and developed the SOIL software in Delphi for the Structural Engineering Society of New Zealand (SESOC).

\section{EDUCATION}
\vspace{0.1in} 
Software Education Associates Ltd,\\
Advanced C++ Programming, 8-10 June 2009

The University of Auckland,\\
Master of Science with First Class Honours,\\
in Computer Science, 2004 
 
The University of Auckland,\\
Bachelor of Technology with First Class Honours,\\
in Information Technology, 2000-2003 
 
Lynfield College, 1998-1999 

\section{PUBLICATIONS} 
\vspace{0.1in}

"Improved Billboard Clouds for Extreme Model Simplification". In-Tai Huang, Kevin Novins and Burkhard Wuensche, \textit{in Proceedings of IVCNZ '04}, Akaroa, New Zealand, 21-23 November 2004, pp. 255-260. 

"Improved Billboard Clouds for Extreme Model Simplification". In-Tai Huang, MSc thesis, Department of Computer Science, University of Auckland, 2004.

\section{REFEREES} 
\vspace{0.1in}

%Jimmy Lin\\
%Programmer\\
%Right Hemisphere\\
%Ph: 021-2607786
Available upon request.
 
\end{resume}
\end{document}






























